Comparative study of requantization of time-dependent mean-field for pairing dynamics

### 2017-11-26 draft1.2.tex
modified:   draft1.2.tex 	modified:   ref.bib

%\documentclass[11pt]{article}
\documentclass[%
%reprint,
superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose,
preprint,
showpacs,
%preprintnumbers,
nofootinbib,
%nobibnotes,
%bibnotes,
amsmath,amssymb,
%aps,
%pra,
%prb,
prc,
%paper,
%rmp,
%prstab,
%prstper,
%twocolumn,
floatfix ]%
{revtex4-1}

@@

\begin{abstract}
%The time-dependent Hartree-Fock-Bogoliubov (TDHFB) theory is useful
%to study large amplitude collective motion with nuclear superfluidity.
%However, in order to obtain quantal information,
%such as energy eigenvalues and transition matrix elements,
%it is necessary to requantize the mean-field dynamics.
To describe quantal collective phenomena, it is useful
to requantize the time-dependent mean-field dynamics.
We study the time-dependent Hartree-Fock-Boboliubov (TDHFB) theory
for the two-level pairing Hamiltonian, and compare results
of different quantization methods.
The one constructing microscopic wave functions,
using the TDHFB trajectories fulfilling the
Einstein-Brillouin-Keller quantization condition,
turns out to be the most accurate.
The method is based on the stationary-phase approximation
to the path integral.
We also examine the performance of the collective model
%analogous to the Bohr model of the quadrupole vibrations and rotation,
which assumes that the pairing gap parameter is the collective coordinate.
The applicability of the collective model is limited
for the nuclear pairing with a small number of
single-particle levels,
because the pairing gap parameter represents only a half of the
pairing collective space.
\end{abstract}

@@

In principle, the TDHFB dynamics can be applicable to large amplitude motion.
The problem is that it is not easy to determine quantum mechanical 
quantities, such as energy eigenvalues and transition matrix elements,
from the TDHFB trajectories.
In addition, the TDHFB lacks a part of quantum fluctuation
associated with low-eneryg
large amplitude collective motion,
which leads to difficutlties in description of the quantum tunneling
processes, such as spontaneous fission and sub-barrier fusion reaction.
For this purpose,
since the TDHF(B) trajectory corresponds to a classical limit of the path
integral formulation,
the requantization of the mean-field dynamics was
proposed \cite{Neg82,KS80,K81,Rei80}.
It recovers quantum fluctuations missing in the mean-field
level, and possibly enables us to describe large-amplitude collective
tunneling phenomena such as spontaneous fission \cite{Neg82}.
The requantization of the TDHFB is particularly feasible
for integrable systems, because the system is described by separable
action-angle variables $(I_k, \phi_k)$, leading to
the Einstein-Brillouin-Keller (EBK) quantization condition.
However, for nonintegrable systems in general, it is difficult to find
suitable periodic orbits to quantize.
A possible solution to this difficulty is to find a decoupled collective
subspace spanned by
a single coordinate and its conjugate momentum \cite{NMMY16}.
Since the one-dimensional system is integrable, the quantization is
practicable.

Another somewhat phenomenological approach
to nuclear collective dynamics is the collective model.
In this approach, the collective Hamiltonian is constructed by choosing
collective coordinates intuitively.
The nuclear energy density functional model is often used as a tool for
a microscopic derivation of the collective Hamiltonian \cite{NMMY16}.
The most well-known and successful model is the Bohr model \cite{BM75},
which was introduced to describe low-energy
nuclear collective motion in quadrupole degrees of freedom with
the deformation parameters $(\beta, \gamma)$ and the Euler angles
$(\alpha,\beta,\gamma)$.
For the pairing motion, the collective coordinates are analogously
chosen as the pair deformation (gap) $\Delta$ and the gauge angle $\Phi$
\cite{BBPK70}.
Based on the pairing collective Hamiltonian, 
effects of the pair motion on the quadrupole vibrations %and fission half lives
have been discussed in literatures \cite{delta1,delta3}.
%\cite{delta1,delta2,delta3}. 
However, it is not trivial whether the pair deformation is really a suitable
choice for the collective coordinate,
which should be investigated in a microscopic approach based on
the TDHFB dynamics.

@@

The paper is organized as follows. 
In Sec. \ref{sec:TDHFB},
we derive a TDHFB classical Hamiltonian for the pairing model.
In Sec. \ref{sec:requantization}, 
the requantization of the TDHFB is performed using different methods,
based on the canonical and the EBK quantizations.
In Sec. \ref{sec:results}, 
the numerical results for the two-level model are shown and compared with
exact results.
Properties of the pairing collective coordinate is also discussed.
We give a conclusion in Sec. \ref{sec:conclusion}.

@@

The Hamiltonian of the pairing model is given in terms of
single-particle energies $\epsilon_l$ and the pairing strength $g$ as
\begin{equation}
%  H &= \sum_l \epsilon_l n_l - \frac{g}{4} \sum_{ll'} P_l^{\dag}P_{l'}
	H = \sum_l \epsilon_l n_l - g \sum_{l,l'} S_l^+ S_{l'}^-
    = \sum_l\epsilon_l(2S_l^0+\Omega_l) - g S^+ S^{-} ,
\end{equation}
where we use the SU(2) quasispin operators,
$\boldsymbol{S}=\sum_l \boldsymbol{S}_l$, with
\begin{eqnarray}
        S_l^0 &=& \frac{1}{2}(\sum_ma_{lm}^{\dag}a_{lm}-\Omega_l) ,\\
        S_l^{+} &=& \sum_{m>0}a_{lm}^{\dag}a_{l\overline{m}}^{\dag} ,
\quad   S_l^{-} = S_l^{+\dag} .
\end{eqnarray}
Each single-particle energy $\epsilon_l$ possesses $(2\Omega_l)$-fold
degeneracy ($\Omega_l=j_l+1/2$)
and $\sum_{m>0}$ indicates the summation over $m=1/2,3/2,\cdots,\Omega_l-1/2$.
The occupation number of each level $l$ is given by
$
	n_l = \sum_m a^{\dag}_{lm}a_{lm} = 2S_l^0+\Omega_l ,
$.
%The first term giving a spherical single particle energy $\epsilon_l$ for each j-shell, which 
The quasispin operators satisfy the commutation relations
\begin{equation}
  [S_l^0,S_{l'}^{\pm}] = \pm\delta_{ll'}S_{l}^{\pm},
	\quad [S_{l}^{+},S_{l'}^{-}] = 2\delta_{ll'}S_{l}^{0} .
\end{equation}
The magnitude of quasispin for each level is
$S_l=\frac{1}{2}(\Omega_l-\nu_l)$, where $\nu_l$ is the seniority
quantum number, namely the number of unpaired particle at each level $l$.
%We call $\nu=\sum_l \nu_l=0$ excited states as pairing collective excited states. The pairing collective excited states can be simple $2p2h, 4p4h\cdots$ excitation or the complex combination of $2p2h, 4p4h\cdots$ components.
In the present study, we only consider seniority zero states with
$\nu=\sum_l \nu_l=0$.
The residual two-body interaction only consists of monopole pairing
interaction which couples two particles to zero angular momentum.
We obtain exact solutions either by solving Richardson equation
\cite{Richardson,Richardson2,Richardson3} or
by diagonalizing the Hamiltonian using the quasispin symmetry.

@@

The coherent state for the seniority $\nu=0$ states
($S_l=\Omega_l/2$) is constructed as
\begin{equation}
	\ket{Z(t)} = \prod_{l} \left(1+|Z_l(t)|^2\right)^{-\Omega_l/2}
	\exp (Z_l(t) S_l^{+}) \ket{0}
 \label{coherent}
\end{equation}
where $\ket{0}$ is the vacuum (zero particle) state,
$Z_l(t)$ are time-dependent complex variables which describe
motion of the system. 
In the SU(2) quasispin representation,
$\ket{0}=\prod_l \ket{S_l,-S_l}$.
The coherent state $\ket{Z(t)}$ is a superposition of
states with different particle numbers
without unpaired particles.
%If $Z_l$ are all real,
In the present pairing model,
the coherent state is the same as the time-dependent BCS wave function
with $Z_l(t)=v_l(t)/u_l(t)$,
where $(u_l(t),v_l(t))$ are the time-dependent BCS $u,v$ factors.

The TDHFB equation can be derived from the tiem-dependent variational
principle,
\begin{equation}
	\delta \mathcal{S} = 0,
	\quad
%  \delta \int \braket{\phi(t)|i\frac{\partial}{\partial t}-H|\phi(t)}dt = 0 ,
	\mathcal{S}\equiv
	\int \braket{\phi(t)|i\frac{\partial}{\partial t}-H|\phi(t)}dt,
  \label{TDHFB}
\end{equation}
where $\ket{\phi(t)}$ is the time-dependent generalized Slater determinant.
In the present case, we adopt the coherent state of Eq. (\ref{coherent}),
$\ket{\phi(t)}=\ket{Z(t)}$.
%Keeping the time-dependent state vector fulfills normalization $\braket{Z|Z}=1$, 
The action $\mathcal{S}$ is
\begin{equation}
	\mathcal{S}  = \int \mathcal{L}(t) dt
	%&= \int \braket{\phi(t)|i\frac{\partial}{\partial t}-H|\phi(t)}dt \\
	= \int dt \left\{ \frac{i}{2} \sum_l \frac{\Omega_l}{1+|Z_l|^2}
  (Z_l^*\dot{Z_l}-Z_l\dot{Z_l^*}) - \braket{Z|H|Z} \right\} ,
\label{S}
\end{equation}
and
\begin{align}
%  \braket{Z|H|Z} &= \sum_l \epsilon_l \left\{ 2S_l\left( 1-\frac{2}{1+|Z_l|^2} \right) + \Omega_l \right\}
%  -g \sum_l \frac{2S_l|Z_l|^2(2S_l+|Z_l|^2)}{(1+|Z_l|^2)^2}
%  -g \sum_{l_1 \neq l_2} \frac{2S_{l_1}Z_{l_1}}{1+|Z_{l_1}|^2}\frac{2S_{l_2}Z_{l_2}^*}{1+|Z_{l_2}|^2}.
  \braket{Z|H|Z} &= \sum_l \epsilon_l \frac{2\Omega_l |Z_l|^2}{1+|Z_l|^2}
  -g \sum_l \frac{\Omega_l|Z_l|^2(\Omega_l+|Z_l|^2)}{(1+|Z_l|^2)^2}
  -g \sum_{l_1 \neq l_2} \frac{\Omega_{l_1}Z_{l_1}}{1+|Z_{l_1}|^2}\frac{\Omega_{l_2}Z_{l_2}^*}{1+|Z_{l_2}|^2}.
	\label{TDHFB_Hamiltonian_1}
\end{align}
We transform the complex variables $Z_l$ into real variables $(q_l,\chi_l)$
by $Z_l = \tan{\frac{\theta_l}{2}}e^{-i\chi_l}$ and $q_l=\cos{\theta_l}$.
The Lagrangian $\mathcal{L}$ and the expectation value of Hamiltonian become
\begin{align}
\mathcal{L}(t) &= \sum_l \frac{\Omega_l}{2}
	(1-q_l)\dot{\chi_l} - \mathcal{H}(Z,Z^*) ,\\
	\mathcal{H}(Z,Z^*)&\equiv \braket{Z|H|Z} = \sum_l \epsilon_l\Omega_l(1- q_l) - \frac{g}{4}\sum_l \Omega_l (\Omega_l(1-q_l^2)+(1-q_l)^2) \nonumber \\
&- \frac{g}{4}\sum_{l_1\neq l_2} \Omega_{l_1}\Omega_{l_2}\sqrt{(1-q_{l_1}^2)(1-q_{l_2}^2)}e^{-i(\chi_{l_1}-\chi_{l_2})}   .
\label{TDHFB_Hamiltonian_2}
\end{align}
Here, $\chi_l$ represent a kind of gauge angle of each level,
and $q_l$ are related to the occupation probability, $q_l=|u_l|^2-|v_l|^2$.
If we choose $\chi_l$ as canonical coordinates, their conjugate momenta
are given by
$p_l\equiv \partial\mathcal{H}/\partial\dot{\chi}_l=\Omega_l(1-q_l)/2$.
Since the Hamiltonian (\ref{TDHFB_Hamiltonian_2}) depends only on
relative difference in the gauge angles,
the ``global'' gauge angles, $\Phi\propto\sum_l \chi_l$,
is a cyclic variable.

@@

Starting an arbitrary state $\ket{\psi(0)}$ at time $t=0$,
the time-dependent full quantum state can be written in the path integral form
\begin{equation}
\ket{\psi(t)}
	= e^{-iHt} \ket{\psi(0)}
	= \int d\mu(Z'') \ket{Z''} \int d\mu(Z')
	\int_{Z(0)=Z'}^{Z(t)=Z''} \mathcal{D}\mu[Z(\tau)])
	e^{i\mathcal{S}[Z(\tau)]} \psi(Z') ,
\label{path_integral_expression}
\end{equation}
where $\psi(Z)\equiv \braket{Z|\psi(0)}$ and
the invariant measure $d\mu(Z)$ is defiend by 
the unity condition,
\begin{equation}
  \int d\mu(Z) \ket{Z}\bra{Z} = 1 .
  \label{unity}
\end{equation}
In Eq. (\ref{path_integral_expression}),
$\mathcal{S}[Z(\tau)]$ is the action (\ref{S}) along a given path $Z(\tau)$
with the initial coherent state $\ket{Z(0)}=\ket{Z'}$ and
the final state $\ket{Z(t)}=\ket{Z''}$,
then, the integration $\int \mathcal {D}\mu[Z(\tau)]$
is performed over all possible paths $\ket{Z(\tau)}$ between them.
Among all trajectories in the path integral,
the lowest stationary phase approximation selects
the TDHFB (classical) trajectories.
%\begin{align}
%	\int \mathcal{D}\mu(Z) e^{i\mathcal{S}(Z,Z_0)} \approx e^{i\mathcal{S}_{\rm cl}(Z,Z_0)} .
%\end{align}
\begin{equation}
	\ket{\psi(t)} \approx \int d\mu(Z') \ket{Z'_{\rm cl}(t)}
	e^{i\mathcal{S}_{\rm cl}(Z'_{\rm cl}(t),Z')} \psi(Z') ,
	\label{SPA}
\end{equation}
where the TDHFB trajectory starting from $\ket{Z'}$
ends at $\ket{Z'_{\rm cl}(t)}$ at time $t$.
The action $\mathcal{S}_{\rm cl}(Z_f,Z_i)$ is calculated along this
classical trajectory
connecting $Z_i=Z'_{\rm cl}(0)=Z'$ and $Z_f=Z'_{\rm cl}(t)$.
\begin{equation}
	\mathcal{S}_{\rm cl}(Z'_{\rm cl}(t),Z') \equiv \int_{0}^{t}
\braket{Z_{\rm cl}(t)|
	i\frac{\partial}{\partial t} - H
	|Z_{\rm cl}(t)} dt
	= \mathcal{T}[Z_{\rm cl}] - \mathcal{H}(Z',Z'^*) t 
	,
	\label{S_cl}
\end{equation}
with
\begin{equation}
\mathcal{T}[Z_{\rm cl}]\equiv
\int_{0}^{t} \braket{Z_{\rm cl}(t)| i\frac{\partial}{\partial t}
	|Z_{\rm cl}(t)} dt 
	= \int_{Z'}^{Z'_{\rm cl}(t)}
	\frac{i}{2} \sum_l \frac{\Omega_l}{1+|Z_l|^2}
  (Z_l^* dZ_l - Z_l dZ_l^*) .
\end{equation}
In the last equation of Eq. (\ref{S_cl}),
we used the fact that the TDHFB trajectory conserves the energy,
$\mathcal{H}(Z_{\rm cl}(t),Z_{\rm cl}^*(t))= \mathcal{H}(Z',Z'^*)$.
%We assume that only classical (TDHFB) trajectory contributes to the time dependent wave function

@@

Finding TDHFB trajectories satisfying the quantization condition
(\ref{EBK}) is an extremenly difficult task in general.
It is better founded and more practical
if the classical system is completely integrable.
In integrable systems, $M$ complex variables $Z(t)$ can be transformed into
the action-angle variables;
\begin{equation}
	Z(t) = \{Z_l(t);l=1,\cdots,M \} \rightarrow
	\{E; v_1,\cdots,v_{M-1}; \theta_1(t),\cdots,\theta_M(t)\} ,
\end{equation}
where the variables $E$ and $v$ define an invariant torus,
while $\theta(t)$ parameterize the coordinates on the torus.
The integration path of Eq. (\ref{EBK}) is now taken as topologically
independent closed path on the torus,
namely the EBK quantization condition.
There are $M$ independent closed paths and $M$ quantum numbers,
$k=(k_1,\cdots,k_M)$, to specify the stationary energy eigenstate.
These are associated with $M$ invariant variables,
$\{E_k;v_1^{(k)},\cdots,v_{M-1}^{(k)}\}$.
Using the invariant measure
\begin{align}
%  d\mu(Z) = \rho(Z)dEdv_1\cdots dv_{M-1}d\theta_1\cdots d\theta_M,
  d\mu(Z) = \rho(E,v,\theta) dEdv_1\cdots dv_{M-1}d\theta_1\cdots d\theta_M,
\end{align}
the $k$-th semiclassical wave function can be calculated as
\begin{equation}
  \ket{\phi_k} \propto \oint d\theta_1\cdots \oint d\theta_M \ 
	\rho(E_k,v^{(k)},\theta)
	\ket{E_k,v^{(k)},\theta} e^{i\mathcal{T}[E_k,v^{(k)},\theta]} .
  \label{semi_wave_func}
\end{equation}
Here, we omit the integration with respect to the invariant variables,
$E$ and $v$.

@@

We apply the requantization methods in Sec.~\ref{sec:requantization}.
In the following, the stationary-phase approximation to the path
integral in Sec.~\ref{sec:SPA} is denoted as ``SPA'',
the Fourier decomposition method (Sec.~\ref{sec:Fourier}) as ``FD'',
and the canonical quantization with periodic boundary condition 
(Sec.~\ref{subsec:canonical1}) as ``CQ''.
%In addition, the harmonic approximation at the ground state is called ''HA''.
Note that the SPA and the FD produce the same eigenenergies which
are based on the EBK quantization rule.

>>>>

%\documentclass[11pt]{article}
\documentclass[%
%reprint,
superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose,
preprint,
showpacs,
%preprintnumbers,
nofootinbib,
%nobibnotes,
%bibnotes,
amsmath,amssymb,
aps,
%pra,
%prb,
prc,
%paper,
%rmp,
%prstab,
%prstper,
%twocolumn,
floatfix ]%
{revtex4-1}

@@

\begin{abstract}
%The time-dependent Hartree-Fock-Bogoliubov (TDHFB) theory is useful
%to study large amplitude collective motion with nuclear superfluidity.
%However, in order to obtain quantal information,
%such as energy eigenvalues and transition matrix elements,
%it is necessary to requantize the mean-field dynamics.
To describe quantal collective phenomena, it is useful
to requantize the time-dependent mean-field dynamics.
We study the time-dependent Hartree-Fock-Bogoliubov (TDHFB) theory
for the two-level pairing Hamiltonian, and compare results
of different quantization methods.
The one constructing microscopic wave functions,
using the TDHFB trajectories fulfilling the
Einstein-Brillouin-Keller quantization condition,
turns out to be the most accurate.
The method is based on the stationary-phase approximation
to the path integral.
We also examine the performance of the collective model
%analogous to the Bohr model of the quadrupole vibrations and rotation,
which assumes that the pairing gap parameter is the collective coordinate.
The applicability of the collective model is limited
for the nuclear pairing with a small number of
single-particle levels,
because the pairing gap parameter represents only a half of the
pairing collective space.
\end{abstract}

@@

In principle, the TDHFB dynamics can be applicable to large amplitude motion.
The problem is that it is not easy to determine quantum mechanical 
quantities, such as energy eigenvalues and transition matrix elements,
from the TDHFB trajectories.
In addition, the TDHFB lacks a part of quantum fluctuation
associated with low-energy
large amplitude collective motion,
which leads to difficulties in description of the quantum tunneling
processes, such as spontaneous fission and sub-barrier fusion reaction.
For this purpose,
since the TDHF(B) trajectory corresponds to a classical limit of the path
integral formulation,
the requantization of the mean-field dynamics was
proposed \cite{Neg82,KS80,K81,Rei80}.
It recovers quantum fluctuations missing in the mean-field
level, and possibly enables us to describe large-amplitude collective
tunneling phenomena such as spontaneous fission \cite{Neg82}.
The requantization of the TDHFB is particularly feasible
for integrable systems, because the system is described by separable
action-angle variables $(I_k, \phi_k)$, leading to
the Einstein-Brillouin-Keller (EBK) quantization condition.
However, for nonintegrable systems in general, it is difficult to find
suitable periodic orbits to quantize.
A possible solution to this difficulty is to find a decoupled collective
subspace spanned by
a single coordinate and its conjugate momentum \cite{NMMY16}.
Since the one-dimensional system is integrable, the quantization is
practicable.

Another somewhat phenomenological approach
to nuclear collective dynamics is the collective model.
In this approach, the collective Hamiltonian is constructed by choosing
collective coordinates intuitively.
The nuclear energy density functional model is often used as a tool for
a microscopic derivation of the collective Hamiltonian \cite{NMMY16}.
The most well-known and successful model is the Bohr model \cite{BM75},
which was introduced to describe low-energy
nuclear collective motion in quadrupole degrees of freedom with
the deformation parameters $(\beta, \gamma)$ and the Euler angles
$(\alpha,\beta,\gamma)$.
For the pairing motion, the collective coordinates are analogously
chosen as the pair deformation (gap) $\Delta$ and the gauge angle $\Phi$
\cite{BBPK70}.
Based on the pairing collective Hamiltonian, 
effects of the pair motion on the quadrupole vibrations %and fission half lives
have been discussed in literature \cite{delta1,delta3}.
%\cite{delta1,delta2,delta3}. 
However, it is not trivial whether the pair deformation is really a suitable
choice for the collective coordinate,
which should be investigated in a microscopic approach based on
the TDHFB dynamics.

@@

The paper is organized as follows. 
In Sec. \ref{sec:TDHFB},
we derive a TDHFB classical Hamiltonian for the pairing model.
In Sec. \ref{sec:requantization}, 
the requantization of the TDHFB is performed using different methods,
based on the canonical and the EBK quantization.
In Sec. \ref{sec:results}, 
the numerical results for the two-level model are shown and compared with
exact results.
Properties of the pairing collective coordinate is also discussed.
We give a conclusion in Sec. \ref{sec:conclusion}.

@@

The Hamiltonian of the pairing model is given in terms of
single-particle energies $\epsilon_l$ and the pairing strength $g$ as
\begin{equation}
%  H &= \sum_l \epsilon_l n_l - \frac{g}{4} \sum_{ll'} P_l^{\dag}P_{l'}
	H = \sum_l \epsilon_l n_l - g \sum_{l,l'} S_l^+ S_{l'}^-
    = \sum_l\epsilon_l(2S_l^0+\Omega_l) - g S^+ S^{-} ,
\end{equation}
where we use the SU(2) quasi-spin operators,
$\boldsymbol{S}=\sum_l \boldsymbol{S}_l$, with
\begin{eqnarray}
        S_l^0 &=& \frac{1}{2}(\sum_ma_{lm}^{\dag}a_{lm}-\Omega_l) ,\\
        S_l^{+} &=& \sum_{m>0}a_{lm}^{\dag}a_{l\overline{m}}^{\dag} ,
\quad   S_l^{-} = S_l^{+\dag} .
\end{eqnarray}
Each single-particle energy $\epsilon_l$ possesses $(2\Omega_l)$-fold
degeneracy ($\Omega_l=j_l+1/2$)
and $\sum_{m>0}$ indicates the summation over $m=1/2,3/2,\cdots,\Omega_l-1/2$.
The occupation number of each level $l$ is given by
$
	n_l = \sum_m a^{\dag}_{lm}a_{lm} = 2S_l^0+\Omega_l ,
$.
%The first term giving a spherical single particle energy $\epsilon_l$ for each j-shell, which 
The quasi-spin operators satisfy the commutation relations
\begin{equation}
  [S_l^0,S_{l'}^{\pm}] = \pm\delta_{ll'}S_{l}^{\pm},
	\quad [S_{l}^{+},S_{l'}^{-}] = 2\delta_{ll'}S_{l}^{0} .
\end{equation}
The magnitude of quasi-spin for each level is
$S_l=\frac{1}{2}(\Omega_l-\nu_l)$, where $\nu_l$ is the seniority
quantum number, namely the number of unpaired particle at each level $l$.
%We call $\nu=\sum_l \nu_l=0$ excited states as pairing collective excited states. The pairing collective excited states can be simple $2p2h, 4p4h\cdots$ excitation or the complex combination of $2p2h, 4p4h\cdots$ components.
In the present study, we only consider seniority zero states with
$\nu=\sum_l \nu_l=0$.
The residual two-body interaction only consists of monopole pairing
interaction which couples two particles to zero angular momentum.
We obtain exact solutions either by solving Richardson equation
\cite{Richardson,Richardson2,Richardson3} or
by diagonalizing the Hamiltonian using the quasi-spin symmetry.

@@

The coherent state for the seniority $\nu=0$ states
($S_l=\Omega_l/2$) is constructed as
\begin{equation}
	\ket{Z(t)} = \prod_{l} \left(1+|Z_l(t)|^2\right)^{-\Omega_l/2}
	\exp (Z_l(t) S_l^{+}) \ket{0}
 \label{coherent}
\end{equation}
where $\ket{0}$ is the vacuum (zero particle) state,
$Z_l(t)$ are time-dependent complex variables which describe
motion of the system. 
In the SU(2) quasi-spin representation,
$\ket{0}=\prod_l \ket{S_l,-S_l}$.
The coherent state $\ket{Z(t)}$ is a superposition of
states with different particle numbers
without unpaired particles.
%If $Z_l$ are all real,
In the present pairing model,
the coherent state is the same as the time-dependent BCS wave function
with $Z_l(t)=v_l(t)/u_l(t)$,
where $(u_l(t),v_l(t))$ are the time-dependent BCS $u,v$ factors.

The TDHFB equation can be derived from the time-dependent variational
principle,
\begin{equation}
	\delta \mathcal{S} = 0,
	\quad
%  \delta \int \braket{\phi(t)|i\frac{\partial}{\partial t}-H|\phi(t)}dt = 0 ,
	\mathcal{S}\equiv
	\int \braket{\phi(t)|i\frac{\partial}{\partial t}-H|\phi(t)}dt,
  \label{TDHFB}
\end{equation}
where $\ket{\phi(t)}$ is the time-dependent generalized Slater determinant.
In the present case, we adopt the coherent state of Eq. (\ref{coherent}),
$\ket{\phi(t)}=\ket{Z(t)}$.
%Keeping the time-dependent state vector fulfills normalization $\braket{Z|Z}=1$, 
The action $\mathcal{S}$ is
\begin{equation}
	\mathcal{S}  = \int \mathcal{L}(t) dt
	%&= \int \braket{\phi(t)|i\frac{\partial}{\partial t}-H|\phi(t)}dt \\
	= \int dt \left\{ \frac{i}{2} \sum_l \frac{\Omega_l}{1+|Z_l|^2}
  (Z_l^*\dot{Z_l}-Z_l\dot{Z_l^*}) - \braket{Z|H|Z} \right\} ,
\label{S}
\end{equation}
and
\begin{align}
%  \braket{Z|H|Z} &= \sum_l \epsilon_l \left\{ 2S_l\left( 1-\frac{2}{1+|Z_l|^2} \right) + \Omega_l \right\}
%  -g \sum_l \frac{2S_l|Z_l|^2(2S_l+|Z_l|^2)}{(1+|Z_l|^2)^2}
%  -g \sum_{l_1 \neq l_2} \frac{2S_{l_1}Z_{l_1}}{1+|Z_{l_1}|^2}\frac{2S_{l_2}Z_{l_2}^*}{1+|Z_{l_2}|^2}.
  \braket{Z|H|Z} &= \sum_l \epsilon_l \frac{2\Omega_l |Z_l|^2}{1+|Z_l|^2}
  -g \sum_l \frac{\Omega_l|Z_l|^2(\Omega_l+|Z_l|^2)}{(1+|Z_l|^2)^2}
  -g \sum_{l_1 \neq l_2} \frac{\Omega_{l_1}Z_{l_1}}{1+|Z_{l_1}|^2}\frac{\Omega_{l_2}Z_{l_2}^*}{1+|Z_{l_2}|^2}.
	\label{TDHFB_Hamiltonian_1}
\end{align}
We transform the complex variables $Z_l$ into real variables $(q_l,\chi_l)$
by $Z_l = \tan{\frac{\theta_l}{2}}e^{-i\chi_l}$ and $q_l=\cos{\theta_l}$.
The Lagrangian $\mathcal{L}$ and the expectation value of Hamiltonian become
\begin{align}
\mathcal{L}(t) &= \sum_l \frac{\Omega_l}{2}
	(1-q_l)\dot{\chi_l} - \mathcal{H}(Z,Z^*) ,\\
	\mathcal{H}(Z,Z^*)&\equiv \braket{Z|H|Z} = \sum_l \epsilon_l\Omega_l(1- q_l) - \frac{g}{4}\sum_l \Omega_l (\Omega_l(1-q_l^2)+(1-q_l)^2) \nonumber \\
&- \frac{g}{4}\sum_{l_1\neq l_2} \Omega_{l_1}\Omega_{l_2}\sqrt{(1-q_{l_1}^2)(1-q_{l_2}^2)}e^{-i(\chi_{l_1}-\chi_{l_2})}   .
\label{TDHFB_Hamiltonian_2}
\end{align}
Here, $\chi_l$ represent a kind of gauge angle of each level,
and $q_l$ are related to the occupation probability, $q_l=|u_l|^2-|v_l|^2$.
If we choose $\chi_l$ as canonical coordinates, their conjugate momenta
are given by
$p_l\equiv \partial\mathcal{H}/\partial\dot{\chi}_l=\Omega_l(1-q_l)/2$.
Since the Hamiltonian (\ref{TDHFB_Hamiltonian_2}) depends only on
relative difference in the gauge angles,
the ``global'' gauge angles, $\Phi\propto\sum_l \chi_l$,
is a cyclic variable.

@@

Starting an arbitrary state $\ket{\psi(0)}$ at time $t=0$,
the time-dependent full quantum state can be written in the path integral form
\begin{equation}
\ket{\psi(t)}
	= e^{-iHt} \ket{\psi(0)}
	= \int d\mu(Z'') \ket{Z''} \int d\mu(Z')
	\int_{Z(0)=Z'}^{Z(t)=Z''} \mathcal{D}\mu[Z(\tau)])
	e^{i\mathcal{S}[Z(\tau)]} \psi(Z') ,
\label{path_integral_expression}
\end{equation}
where $\psi(Z)\equiv \braket{Z|\psi(0)}$ and
the invariant measure $d\mu(Z)$ is defined by 
the unity condition,
\begin{equation}
  \int d\mu(Z) \ket{Z}\bra{Z} = 1 .
  \label{unity}
\end{equation}
In Eq. (\ref{path_integral_expression}),
$\mathcal{S}[Z(\tau)]$ is the action (\ref{S}) along a given path $Z(\tau)$
with the initial coherent state $\ket{Z(0)}=\ket{Z'}$ and
the final state $\ket{Z(t)}=\ket{Z''}$,
then, the integration $\int \mathcal {D}\mu[Z(\tau)]$
is performed over all possible paths $\ket{Z(\tau)}$ between them.
Among all trajectories in the path integral,
the lowest stationary phase approximation selects
the TDHFB (classical) trajectories.
%\begin{align}
%	\int \mathcal{D}\mu(Z) e^{i\mathcal{S}(Z,Z_0)} \approx e^{i\mathcal{S}_{\rm cl}(Z,Z_0)} .
%\end{align}
\begin{equation}
	\ket{\psi(t)} \approx \int d\mu(Z') \ket{Z'_{\rm cl}(t)}
	e^{i\mathcal{S}_{\rm cl}(Z'_{\rm cl}(t),Z')} \psi(Z') ,
	\label{SPA}
\end{equation}
where the TDHFB trajectory starting from $\ket{Z'}$
ends at $\ket{Z'_{\rm cl}(t)}$ at time $t$.
The action $\mathcal{S}_{\rm cl}(Z_f,Z_i)$ is calculated along this
classical trajectory
connecting $Z_i=Z'_{\rm cl}(0)=Z'$ and $Z_f=Z'_{\rm cl}(t)$.
\begin{equation}
	\mathcal{S}_{\rm cl}(Z'_{\rm cl}(t),Z') \equiv \int_{0}^{t}
\braket{Z_{\rm cl}(t)|
	i\frac{\partial}{\partial t} - H
	|Z_{\rm cl}(t)} dt
	= \mathcal{T}[Z_{\rm cl}] - \mathcal{H}(Z',Z'^*) t 
	,
	\label{S_cl}
\end{equation}
with
\begin{equation}
\mathcal{T}[Z_{\rm cl}]\equiv
\int_{0}^{t} \braket{Z_{\rm cl}(t)| i\frac{\partial}{\partial t}
	|Z_{\rm cl}(t)} dt 
	= \int_{Z'}^{Z'_{\rm cl}(t)}
	\frac{i}{2} \sum_l \frac{\Omega_l}{1+|Z_l|^2}
  (Z_l^* dZ_l - Z_l dZ_l^*) .
\end{equation}
In the last equation of Eq. (\ref{S_cl}),
we used the fact that the TDHFB trajectory conserves the energy,
$\mathcal{H}(Z_{\rm cl}(t),Z_{\rm cl}^*(t))= \mathcal{H}(Z',Z'^*)$.
%We assume that only classical (TDHFB) trajectory contributes to the time dependent wave function

@@

Finding TDHFB trajectories satisfying the quantization condition
(\ref{EBK}) is an extremely difficult task in general.
It is better founded and more practical
if the classical system is completely integrable.
In integrable systems, $M$ complex variables $Z(t)$ can be transformed into
the action-angle variables;
\begin{equation}
	Z(t) = \{Z_l(t);l=1,\cdots,M \} \rightarrow
	\{E; v_1,\cdots,v_{M-1}; \theta_1(t),\cdots,\theta_M(t)\} ,
\end{equation}
where the variables $E$ and $v$ define an invariant torus,
while $\theta(t)$ parameterize the coordinates on the torus.
The integration path of Eq. (\ref{EBK}) is now taken as topologically
independent closed path on the torus,
namely the EBK quantization condition.
There are $M$ independent closed paths and $M$ quantum numbers,
$k=(k_1,\cdots,k_M)$, to specify the stationary energy eigenstate.
These are associated with $M$ invariant variables,
$\{E_k;v_1^{(k)},\cdots,v_{M-1}^{(k)}\}$.
Using the invariant measure
\begin{align}
%  d\mu(Z) = \rho(Z)dEdv_1\cdots dv_{M-1}d\theta_1\cdots d\theta_M,
  d\mu(Z) = \rho(E,v,\theta) dEdv_1\cdots dv_{M-1}d\theta_1\cdots d\theta_M,
\end{align}
the $k$-th semiclassical wave function can be calculated as
\begin{equation}
  \ket{\phi_k} \propto \oint d\theta_1\cdots \oint d\theta_M \ 
	\rho(E_k,v^{(k)},\theta)
	\ket{E_k,v^{(k)},\theta} e^{i\mathcal{T}[E_k,v^{(k)},\theta]} .
  \label{semi_wave_func}
\end{equation}
Here, we omit the integration with respect to the invariant variables,
$E$ and $v$.

@@

We apply the requantization methods in Sec.~\ref{sec:requantization}.
In the following, the stationary-phase approximation to the path
integral in Sec.~\ref{sec:SPA} is denoted as ``SPA'',
the Fourier decomposition method (Sec.~\ref{sec:Fourier}) as ``FD'',
and the canonical quantization with periodic boundary condition 
(Sec.~\ref{sec:canonical}) as ``CQ''.
%In addition, the harmonic approximation at the ground state is called ''HA''.
Note that the SPA and the FD produce the same eigenenergies which
are based on the EBK quantization rule.
